\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\title{Software Requirements Specification\\Upwork Proposal Assistant}
\author{}
\date{}

\begin{document}

\maketitle

\section{Introduction}
This section defines SRS purpose, scope and organization to make stakeholders understand.

\subsection{Purpose}
This Software Requirements Specification (SRS) document comprehensively defines all Functional requirements (FR) and non-Functional requirements (NFR). It serves as the contractual basis between team and the Requirement Provider (RP), providing the base for system design, implementation, verification, and validation [1,2].

\subsection{Scope}
The Upwork Proposal Assistant shall analyse client profiles from Upwork (hiring rate, budget history, job success rate, reviews, location), generate the proposal templates using past successful submissions, and provide client summary so that the freelancers may decide whether to apply or not. The benefit is that the time wasted in writing proposal is reduced. The job success rate is 3x higher as there is client analysis [3,4].

\subsection{Definitions, Acronyms, and Abbreviations}
\begin{itemize}
    \item RP: Requirement Provider (Faisal Shahzad)
    \item SRS: Software Requirements Specification
    \item FR: Functional Requirement
    \item NFR: Non-Functional Requirement
    \item UI: User Interface
    \item JSR: Job Success Rate
\end{itemize}

All undefined terms confirm to IEEE Std 729-1983 Glossary of Software Engineering Terminology [5].

\section{Overall Description}
This section provides essential context without specifying implementation details or design solutions.

\subsection{Product Perspective}
New standalone browser extension solving the manual Upwork proposal inefficiencies. Unlike generic template tools, it analyses client history (location eligibility, JSR, hourly rates, post format) before generating personalized proposals [3].

\subsection{Product Functions}
The system shall support five major functions:
\begin{itemize}
    \item Client profile analysis (JSR, reviews, location)
    \item Client reliability assessment and decision recommendations
    \item Personalized proposal template generation from past successes
    \item Proposal customization with full freelancer control
    \item Success analytics dashboard
\end{itemize}

\subsection{User Characteristics}
\textbf{Primary users include:}
\begin{itemize}
    \item \textbf{Freelancers} (primary): Intermediate web skills, frequent use, need quick client analysis
    \item \textbf{Administrators}: Advanced skills, manage templates or users
    \item \textbf{Developers}: Project team for maintenance
\end{itemize}

All users have basic browser proficiency.

\subsection{General Constraints}
\begin{itemize}
    \item Browser compatibility: Chrome v100+, Firefox v100+, Edge v100+
    \item No direct Upwork API integration (manual client data input required)
    \item Freelancer data privacy and ethical usage compliance
\end{itemize}

\subsection{Assumptions and Dependencies}
\begin{itemize}
    \item Freelancers manually input accurate client profile data (JSR, client reviews)
    \item RP provides validated client analysis parameters and scoring weights
    \item Users maintain active Upwork accounts
    \item Past successful proposal data available for template training
\end{itemize}

\section{Functional Requirements}
Organized per IEEE Table 2 using ``The system shall...'' format with unique FR-IDs [1].

\subsection{FR-001 Client Profile Analysis}
\subsubsection{Introduction}
The system shall analyse Upwork client profiles and generate reliability scores.

\subsubsection{Inputs}
Client data: JSR (0-100\%), hourly rate (\$0-200), total jobs posted (0-1000), reviews (0-500), location, last activity date, post format.

\subsubsection{Processing}
Calculate reliability score (0-100) using weighted parameters; location eligibility; detect high-risk clients (JSR<30\%); generate decision recommendation.

\subsubsection{Outputs}
Client summary report, reliability score, apply or reject recommendation within 2 seconds.

\subsection{FR-002 Proposal Template Generation}
\subsubsection{Introduction}
The system shall generate personalized proposals matching client requirements and past successes.

\subsubsection{Inputs}
Client summary, job requirements, freelancer's past successful proposals, preferred style.

\subsubsection{Processing}
Match client post format to optimal templates; insert personalized elements (skills, experience); adapt tone to client location or preferences.

\subsubsection{Outputs}
Complete editable proposal draft in professional format.

\subsection{FR-003 Freelancer Decision Support}
\subsubsection{Introduction}
The system shall provide actionable recommendations before proposal submission.

\subsubsection{Inputs}
Client analysis results, freelancer's application resources and time availability.

\subsubsection{Processing}
Risk assessment; Connects cost vs. success probability; time investment analysis.

\subsubsection{Outputs}
Decision matrix: ``Strong Apply'', ``Apply with Caution'', ``Skip''; expected ROI (Return on Investment).

\subsection{FR-004 Template Management}
\subsubsection{Introduction}
The system shall maintain and update proposal templates.

\subsubsection{Inputs}
New successful proposals, RP-approved templates, performance analytics.

\subsubsection{Processing}
Auto-categorize by client type or job category; rank by success rate; suggest improvements.

\subsubsection{Outputs}
Template library with success metrics; admin approval workflow.

\section{References (IEEE Style)}
\begin{enumerate}
    \item IEEE Std 830-1998, \textit{IEEE Recommended Practice for Software Requirements Specifications}, IEEE Computer Society, 1998.
    \item ISO/IEC/IEEE 29148:2018, \textit{Systems and Software Engineering --- Requirements Engineering}, ISO, 2018.
    \item Upwork, ``How to Create a Proposal That Wins Jobs.'' \url{https://www.upwork.com/resources/how-to-create-a-proposal-that-wins-jobs}
    \item M. Al-Razgan et al., ``Artificial Intelligence-Based Text Generation Systems,'' \textit{Applied Sciences}, vol. 12, no. 21, 2022.
    \item IEEE Std 729-1983, \textit{IEEE Glossary of Software Engineering Terminology}, IEEE Computer Society.
\end{enumerate}

\end{document}